Meet the team

### 2025-01-19 team.qmd
update team info

<style>
.team-member {
  display: flex;
  align-items: center;
  padding: 20px; /* Add padding around each team member */
  border: 1px solid #ddd; /* Optional: Add a border for better visual separation */
  margin-bottom: 20px; /* Add space between each team member */
}

.team-img {
  margin-right: 20px;
  width: 175px; /* Set the desired width */
  height: 175px; /* Set the desired height */
  border-radius: 50%; /* Make the image rounded */
  object-fit: cover; /* Ensure the image covers the area */
}

@@

<div class="team-member">
  <img src="images/daniel-deletsu.jpg" alt="images/nour-alfif.jpg" class="team-img">
  <div class="team-info">
  <h4> Daniel Deletsu, B.Sc. </h4>
  <p> M.Sc. Student </p>
  <p> deletsud [at] mcmaster [dot] ca </p>
  </div>
</div>

@@

The lab maintains active and extensive research collaborations with:  
[Joshua Cashaback](https://joshcashaback.weebly.com/) | Department of Biomedical Engineering, University of Delaware  
[Brad Mckay](https://bradmckay-motor-meta.netlify.app/) | Milwaukee Brewers

@@

Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)

>>>>

<style>
.team-member {
  display: flex;
  align-items: center;
  padding: 20px; 
  border: 1px solid #ddd;
  margin-bottom: 20px;
}

.team-img {
  margin-right: 20px;
  width: 175px;
  height: 175px;
  border-radius: 50%;
  object-fit: cover;
}

@@

<div class="team-member">
  <img src="images/daniel-deletsu.jpg" alt="images/daniel-deletsu.jpg" class="team-img">
  <div class="team-info">
  <h4> Daniel Deletsu, B.Sc. </h4>
  <p> M.Sc. Student </p>
  <p> deletsud [at] mcmaster [dot] ca </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Andrea Albert Pravin </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Faris Almoni </h4>
  <p> Undergraduate practicum student </p>
  <p> LIFESCI 4A03 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Gaile Cheng </h4>
  <p> Undergraduate practicum student </p>
  <p> SCIENCE 2RP3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/michael-croteau.jpg" alt="images/michael-croteau.jpg" class="team-img">
  <div class="team-info">
  <h4> Michael Croteau </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Enuri Dissanayake </h4>
  <p> Undergraduate thesis student </p>
  <p> LIFESCI 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Leo Ducharme </h4>
  <p> Undergraduate thesis student </p>
  <p> PNB 4D06 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Tara Esbati </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Shiuli Khanna </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L12 A/B </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Linsea Martin </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/courtney-nguyen.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Courtney Nguyen </h4>
  <p> Undergraduate thesis student </p>
  <p> HTHSCI 4A15 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/shiv-peshwa.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Shiv Peshwa </h4>
  <p> Undergraduate practicum student </p>
  <p> KINESIOL 3RP3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Dana Rugole </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Biochemistry) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/lab-logo.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Nicole Su </h4>
  <p> Undergraduate thesis student </p>
  <p> BIOLOGY 4C12 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/vida-sussman.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Vida Sussman </h4>
  <p> Undergraduate project student </p>
  <p> PNB 3QQ3 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/eshaa-tariq.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Eshaa Tariq </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Kinesiology) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/eleanore-wu.png" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Eleanore Wu </h4>
  <p> Undergraduate research assistant </p>
  <p> Volunteer (Kinesiology) </p>
  </div>
</div>

<div class="team-member">
  <img src="images/jacqueline-zheng.jpg" alt="images/" class="team-img">
  <div class="team-info">
  <h4> Jacqueline Zheng </h4>
  <p> Undergraduate thesis student </p>
  <p> NEUROSCI 4L09 </p>
  </div>
</div>

<div class="team-member">
  <img src="images/headshot_duck-bryan.jpg" alt="images/headshot_duck-bryan.jpg" class="team-img">
  <div class="team-info">
  <h4> Duck Bryan </h4>
  <p> Lab duck </p>
  </div>
</div>

<div class="team-member">
  <img src="images/headshot_duck-joy.jpg" alt="images/headshot_duck-joy.jpg" class="team-img">
  <div class="team-info">
  <h4> Duck Joy </h4>
  <p> Lab duck </p>
  </div>
</div>

<div class="team-member">
  <img src="images/headshot_duck-norris.jpg" alt="images/headshot_duck-norris.jpg" class="team-img">
  <div class="team-info">
  <h4> Duck Norris </h4>
  <p> Lab duck </p>
  </div>
</div>

<div class="team-member">
  <img src="images/headshot_ducky-parton.jpg" alt="images/headshot_ducky-parton.jpg" class="team-img">
  <div class="team-info">
  <h4> Ducky Parton </h4>
  <p> Lab duck </p>
  </div>
</div>

<div class="team-member">
  <img src="images/headshot_lil-quack.jpg" alt="images/headshot_lil-quack.jpg" class="team-img">
  <div class="team-info">
  <h4> Lil Quack </h4>
  <p> Lab duck </p>
  </div>
</div>

@@

The lab maintains active and extensive research collaborations with:  
[Joshua Cashaback](https://joshcashaback.weebly.com/) | Department of Biomedical Engineering, University of Delaware  
[Brad Mckay](https://bradmckay-motor-meta.netlify.app/) | Milwaukee Brewers  
[Jonathan Cannon](https://metre.mcmaster.ca/) | Department of Psychology, Neuroscience, and Behaviour, McMaster University

@@

Aashna Gujral (2024); Dami Alabi Benson (2024); Jacqueline Zheng (2023-24); Abby Girouard (2023-24); Michael Croteau (2024); Aditya Trivedi (2024); Navishka Brahmbhatt (2024); Francesca Caputo (2024); Jil Soni (2024); Enuri Dissanayake (2023); Jeswende Seedu (2022-23); Vivian Li (2022); Caroline Jarvi (2022); Gurlal Gill (2021); Anita Chaseendran (2021); Gianna Jeyarajan (2021); Mackenzie (Kenzie) Bell (2021); Ashton Yuen (2021); Charlie Violin (2021); Ammaar Jan (2020); Faran Chaudhry (2020); Yu (Sarah) Fu (2020); Andrew Poskus (2019); Maya El-Zahed (2019); Grant Yang (2019); Olena Leshchyshen (2019); Rita Waseem (2019); Christian Kleiser (2018); Christopher Li (2018); Faryal Zahir (2018)
